\section{KEY SKILLS}
\begin{itemize}
    \item \textbf{Programming Languages:} Python3 (6+ years), Java (3 years), R (1 year), HTML/CSS (1 year), Python2 (1 year), MySQL (1 year), SQL Oracle (1 year), JavaScript (1 year).
    \item \textbf{Software Systems:} Anaconda, Phpmyadmin, MySQL Workbench, Apache Server 2, Apache Lucene, Apache Spark (6 months back in 2015), Apache JMeter, Oracle VirtualBox, VMWare, Glassfish Server, CMS Tools (i.e. Wordpress, OpenCart, Xcart), LaTeX Overleaf (6+ years).
    \item \textbf{Python Libraries:} scikit-learn, scipy.sparse, NumPy, pandas, beautifulsoup4, PyTorch and more.   
    \item \textbf{IDEs:} Visual Studio Code, NetBeans, Spider and Jupyter Notebook. 
    \item \textbf{Operating Systems:} Mainly Linux Ubuntu and Debian flavors, Windows (10, 7 and Vista) and Unix Solaris.
    \item \textbf{General Purpose Software:} Microsoft Office Suite, Google Docs, Libre Office, Overleaf, PuTTy, FileZilla, WinSCP, FortiClient, BibTeX, OneNote, Slack, Trello, EndNote, Zoom, Microsoft Project, Skype, PSPP.
    \item \textbf{Other Frameworks:} Linux Terminal and Windows PowerShell.
    \item \textbf{Version Control System:} Git.
    \item \textbf{Datasets:} Experienced with the following Datasets and Test Collections: PubMed article data, Movie Lens datasets, Netflix dataset, Blood Transfusion Service dataset (UCI ML repository), CDNOW transactional data set, Titanic and Credit Card Fraud detection datasets (Kaggle repository), NYT 2017 and WP 2018 Common Core collection, Job Shop Scheduling data and more.
    \item \textbf{Soft Skills:} I am a disciplined and dedicated professional who is willing to extend his knowledge base and put in the work necessary to deliver projects on time. In my placement in the Bank of Greece, I displayed organisational and communication skills in assisting teams within the ESSM division.
    \item \textbf{Weaknesses:} Not familiarised with all software development methods. However, I have completed a Software Processes \& Agile Practices course and worked with Agile, Scrum and Waterfall teams.
\end{itemize}