\section{EXPERIENCE}

{\customcventry{November 2020 - Present}{Software Engineer (Full-Time)}{SWORD IT Services Greece S.A.}{Athens, Greece}{}
{\begin{flushleft}
\begin{itemize}
  \item Analyzed, designed and implemented Business Intelligence and Analytics systems.
  \item Migrated existing data pipelines from SAS to Python.
  \item Optimized performance of existing BI & Analytics systems;
  \item Developed ETL flows using Python and SQL/SQL Server.
  \item Implemented best practices working with Jupyter Notebook and eventually GIT, Jenkins etc. for ETL purposes following client’s guidelines.
  \item Setup the back-end environment for ETL following the client’s guidelines.
\end{itemize} 
\end{flushleft} } } 

{\customcventry{March 2020 - March 2021}{Computer Science Teacher and Self-Employed Freelancer (Part-Time)}{Teacherfinder.gr \& Upwork}{Worldwide}{}
{\begin{flushleft}
\begin{itemize}
  \item I taught private lessons to undergraduate and postgraduate students in the following programming languages: Java, Python, R, JavaScript, HTML/CSS, MySQL and Oracle SQL. 
  \item I have been providing technical support services mainly to postgraduate and undergraduate students. These services included designing, solving and coding projects and other exercises. Informatics courses were also delivered for Lyceum students.  
  \item Courses taught physically \& in virtual classroom set up through Skype, Zoom, etc.
\end{itemize} 
\end{flushleft} } } 

{\customcventry{August 2018 - April 2019}{Analyst - Informatics Corps (Full-Time)}{Centre of Information Technology Support of the Hellenic Army}{Athens, Greece}{}
{\begin{flushleft}
\begin{itemize}
  \item Operated the Janus strategy simulation software, the Joint Exercise Management Module (JEMM) and contributed in the interconnection of VBS3, SteelBeast, and JCATS through DIS. Operated monitoring software programs (i.e. Nagios, WhatsUpGold Network monitoring, PRTG). Used simulation software interconnection tools and Excel to perform vlookup operations and produce para-metric spreadsheets and presentations to help allocate land army personnel.
  \item Installed and synchronised an indoor camera with Idomeneus a high-tech software that creates a virtual reality military indoor firing range using lasers and video imagery.
\end{itemize} 
\end{flushleft} } } 

{\customcventry{September 2017 - April 2018}{Java, Python Lab Demonstrator and Exams Assessor (Part-Time)}{University of Strathclyde - UK higher education}{Glasgow, UK}{}
{\begin{flushleft}
Lab Demonstrator and Assessor for Undergraduate and Postgraduate Students at the University of Strathclyde in the Computer and Information Sciences Department. 
\begin{itemize}
\begin{tabular}{ccc}
& a)  \raggedleft Programming Foundations & b) Big Data Fundamentals\\
& c)  \raggedleft Advanced Programming & d) Big Data Technologies\\
\end{tabular}
\end{itemize}
\end{flushleft} } }

{\customcventry{August 2017 - October 2017}{Research Analyst | Improve Newslines pipeline (Full-Time)}{Newslines}{Glasgow, UK}{}
{\begin{flushleft}
\begin{itemize}
    \item Created a ML pipeline to justify a proof of concept. The concept was to reduce editorial time for the development of articles. Text processing on media news stream using Python libraries such as NLTK, BeautifulSoup, os, urllib.request, csv, collections, scikit-learn (naive\_bayes, metrics, svm, discriminant\_analysis, etc.), extractURL, Pandas, NumPy, random, etc. 
    \item Understood the WordPress structure of Newsline's MySQL database for schema objects and their relationships (primary and foreign keys).
    \item Extracted with scripts original source links from summary articles. Fetched automatically the HTML content from the source URLs. Extracted the Title and clean text of articles found on the WWW (removal of HTML tags, etc.).
    \item Extracted named events (e.g. debates, matches) and named entities (e.g. politicians and athletes names) with the Stanford NER toolkit for classification. 
    \item Text feature extraction, tokenisation, build-analysis of text, bag of words representation, common and TF-IDF term weighting vectoriser usage, train and test with ML models (LDA, SVM). The conclusion of my code analysis helped other researchers form a business report (> £21000) for the client to apply for a funding award competition to pursue growth. 
\end{itemize}
\end{flushleft} } }

{\customcventry{July 2015 - July 2016}{Intern in ESSM dept. (Full-Time)}{Central Bank of Greece}{Athens, Greece}{}
{\begin{flushleft}
\begin{itemize}
    \item Participated in the migration to the Target II Security Euro-system.
    \item Used the FT Console System for monitoring components of the Secondary Securities Market Department.
    \item Contributed to the Bonds Report Server System written in VB2012 and participated in the development of an application which facilitated remote access for users in the Dematerialised Securities System division.
    \item Operated in the Test database environment (Oracle SQL).
    \item Manipulated the end-of-day buy/sell back transactions in securities within the Book-Entry Securities System of the Bank of Greece.
    \item Left since I wanted to pursue a Master of Science degree in Glasgow, UK. 
\end{itemize}
\end{flushleft} } }
