\section{WORKSHOPS, CONFERENCES AND CERTIFICATES}
\begin{minipage}{\maincolumnwidth}%
	\small{
    	\begin{itemize}
          \item Big Data Analytics Introduction, JP Morgan Glasgow, May 2017.
          \item FOSSCOMM 2016, University of Piraeus.
          \item Agriculture Development Systems, ATHENA Research Centre, Nov. 2014-2015.
          \item Presentation \& Communication, British Council, Technopolis Innovation Centre, 2014.
          \item SiSRG research group presentations, University of Strathclyde, 2017-Present.
          \item SICSA PhD Conference 2019, University of Stirling, 2019
          \item ICMI 2017, University of Glasgow, Attended this international conference as a Student Volunteer \textit{https://icmi.acm.org/2017/index.php?id=people}
          \item Presented in the "OMAKOION" seminar series. These series were hosting talks in a variety of scientific, military operations and general interest topics.
          \item Software Processes and Agile Practices, Authorised by The University of Alberta \\   See credential: \textit{{https://www.coursera.org/account/accomplishments/certificate/5E4VJ58RYGER}}.
          \item Python Intermediate Certificate from HackeRank Credential ID: A453FSF30B7B \\
          See credential: \textit{https://www.hackerrank.com/certificates/a453f5f30b7b} 
          \item AWS DevDay Online Conference received on October 15, 2020.
          \item Google Cloud Essentials Award received on November 9, 2020.
		\end{itemize}
\end{minipage}